---
title: "Stock Data"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(TTR)
library(quantmod)
library(tidyverse)
```

This notebook will obtain all stock data. You must have run cleanData.rmd and RedditSentiment.Rmd first before moving onto this step. 


Obtaining stock market tickers
```{r}
stockSymbols <- stockSymbols(exchange = c("AMEX", "NASDAQ", "NYSE"), sort.by = c("Exchange",
"Symbol"), quiet = FALSE)

stockSymbols <- stockSymbols %>% 
  mutate(Symbol = tolower(Symbol)) ##%>% 
  ##write.csv(.,'stockTickers.csv', row.names = FALSE) 
```

unique industries - just for reference
```{r eval=FALSE, include=FALSE}
unique(stockSymbols$Industry)
```

Pulling all stock prices by day for specified period. Only pulling prices of the stock tickers used in tickers 
```{r}
#https://stackoverflow.com/questions/48207991/convert-xts-to-data-frame

#manually created list of stocks we are focusing on
tickers <- c("mu","amd","tsla","snap","nvda","fb","amzn","baba","aapl","ge","msft","nflx")

dataEnv <- new.env()
for(company in tickers){
  try(getSymbols(company, auto.assign = TRUE, src="yahoo", from="2018-01-01", to="2018-09-30",return.class = 'zoo', env=dataEnv))
  print(company)
}

plist <- eapply(dataEnv, Ad)
ad.Stocks <- do.call(merge, plist) 


Stockreturns <- data.frame(c(diff(ad.Stocks))) 
StockPrices <- fortify.zoo(ad.Stocks)
Stockreturns.pcnt <- data.frame(c(diff(ad.Stocks)/ad.Stocks[-nrow(ad.Stocks),] )) 

Stockreturns.pcnt <- round(Stockreturns.pcnt,3)


```


Creating final dataframe suitable for modeling in the long format and adds in lagged price changes. 
```{r}
StockPrices <- StockPrices %>% 
  mutate(Date = Index,
         Index = NULL) 

StockPrices_Long <- StockPrices %>% 
  gather(key,value, 1:(length(StockPrices)-1)) %>% 
  group_by(Date, key) %>% 
  rename(stockTicker = key,
         stockPrice = value
  )

StockPricesFinal <- StockPrices_Long %>% 
  group_by(stockTicker) %>% 
  mutate(
    lag1 = lag(stockPrice),
    lag2 = lag(stockPrice,2),
    lag3 = lag(stockPrice,3),
    lag7 = lag(stockPrice,7),
    lag30 = lag(stockPrice,30),
    lag90 = lag(stockPrice,90),
    pct.change1 = round(((stockPrice - lag1) / lag1),3),
    pct.change2 = round(((stockPrice - lag2) / lag2),3),
    pct.change3 = round(((stockPrice - lag3) / lag3),3),
    pct.change7 = round(((stockPrice - lag7) / lag7),3),
    pct.change30 = round(((stockPrice - lag30) / lag30),3),
    pct.change90 = round(((stockPrice - lag90) / lag90),3)
  ) 
  
write.csv(StockPricesFinal, "StockPricesFinal.csv")
  
  

  
```



